### 2015-04-30 inst/examples/vital_rate_fxns_example.Rmd
adds plots of yearly intercepts and slopes for check

# Test of INLA regression fitting functions
```{r libs}
library(communitySynchrony)
library(INLA)
```

@@

>>>>

# Test of INLA regression fitting functions
```{r libs}
library(communitySynchrony)
library(INLA)
library(reshape2)
library(ggplot2)
```

@@

### Plot yearly intercepts and slopes
```{r plots}
intercepts <- matrix(ncol=length(sppList), nrow=nrow(growth_params[[1]]))
slopes <- matrix(ncol=length(sppList), nrow=nrow(growth_params[[1]]))
i <- 1
for(spp in sppList){
  intercepts[,i] <- growth_params[[spp]]$Intercept.yr
  slopes[,i] <- growth_params[[spp]]$logarea.t0.yr
  i <- i+1
}
colnames(intercepts) <- sppList
colnames(slopes) <- sppList
intm <- melt(intercepts)
slopem <- melt(slopes)
intm$variable <- "intercept"
slopem$variable <- "slope"
combo <- rbind(intm, slopem)
ggplot(subset(combo, Var2!="ARTR"), aes(x=Var1, y=value, color=Var2))+
  geom_line()+
  geom_point()+
  facet_grid(variable~., scales="free_y")
```
